Online {\IterComp}

### 2017-09-15 results.tex
minor stuff

In this experiment we evaluate the runtime overhead introduced by the work efficiency profiling. We compile the program using the
{\flagstype -O3}. We then measure the wall-clock time of the instrumented and the native versions to calculate the runtime overhead. For
each benchmark, we compute the average overhead over all its 1,000 inputs.

Figure~\ref{fig:overhead-O3} shows the runtime overhead imposed by the work profiling using each of the instrumentation strategies over
their non-instrumented counterparts. The WPO relaxation was performed using profiling information for every specific input, which provides
the perfect information to perform the WPO relaxation. This means that the experiments show its best performance enabled by having perfect
profiling information.

@@

Finally, as shown in Figure~\ref{fig:error-O3}, these improvements can be
obtained while incurring very little dynamic error.
This result confirms the overly conservative aspect of the relaxation algorithm
applied per DAG, while the WPO relaxation is significantly less conservative.
Although the error bound is not guaranteed by the WPO relaxation,
its dynamic error was always below the 5\% thresholds due to the use
of perfect profiling information.

>>>>

In this experiment we evaluate the runtime overhead introduced by the work efficiency profiling. We compile the program using the
{\flagstype -O3}. We then measure the wall-clock time of the instrumented and the native versions to calculate the runtime overhead. For
each benchmark, we compute the average overhead over all its 1,000 inputs.
Figure~\ref{fig:overhead-O3} shows the runtime overhead imposed by the work profiling using each of the instrumentation strategies over
their non-instrumented counterparts.
%The WPO relaxation was performed using profiling information for every specific input, which provides
%the perfect information to perform the WPO relaxation. This means that the experiments show its best performance enabled by having perfect
%profiling information.

@@

Finally, as shown in Figure~\ref{fig:error-O3}, these improvements can be
obtained while incurring very little dynamic error.
This result confirms the overly conservative aspect of the relaxation algorithm
applied per DAG, while the WPO relaxation is significantly less conservative.
Although the error bound is not guaranteed by the WPO relaxation,
its dynamic error was always below the 5\% thresholds.
%due to the use of perfect profiling information.
